Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-19 RR_manuscript/Draft_RR.Rmd

**Non-preregistered**. However, in our preregistration we did not take into account that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption. 
Teams were explicitly instructed to only submit one effect size without enforcing it. 
As a result, some teams followed the instruction and submitted only one model while others submitted multiple models.
To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id)`), which allows us to estimate both the between-team variation and the between-analysis variation.
This analysis was not preregistered and should thus be interpreted with caution.^[Note that before fitting this model, we fit a separate one in which model ID was the only (non-nested) group-level effect. 
The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.]

@@

After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g. by duration, f0, etc,) or, if they do, they do so by a maximum of `r pm(x = 0.02)` standard units.

**Non-preregistered**. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
In this non-preregistered model, the meta-analytic intercept estimate is between `r round(meta_intercept_nest[3],3)` and `r round(meta_intercept_nest[4],3)` standard units (95\% CrI, $\beta$ = `r round(meta_intercept_nest[1],3)`).
This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95% confidence.
Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).

@@

While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e. are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in blue, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).

@@

Different analysis paths led to different categorical conclusions with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect.
To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows. 
These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to a variegated set of measures, for example the domain "word" includes words that differed along several dimensions, including their length and their metrical structure.]

For example, for those analyses that investigated the duration of vowels (e.g. the duration of the stressed vowel in *Banane*), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to duration values ranging from `r round(min(msa_models$estimate) * 33.4,2) ` to `r round(max(msa_models$estimate) * 51.4,2)` ms.
A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r round(3.8*1.96, 1)` and `r round(7.7*1.96, 1)` ms at 95% credibility.^[The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: $33.4 * 0.11 = 3.8$, $3.8 * 1.96 = 7.4$ ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, times 1.96: $51.4 * 0.15 = 7.7$, $7.7 * 1.96 = 15.1$ ms.]

While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms [@nicenboim2018using]. 
This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against] and has been replicated several times in both production and perception.
Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts [@coretta2019], reduction phenomena [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect]. 
Thus, variation between different analyst teams of `r round(3.8*1.96)` to `r round(7.7*1.96)` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.

@@

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions. 
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates: 
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations. 
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e. mean, mininum, maximum, or range) and how their statistical model was constructed (i.e. the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4). 
As shown by Breznau et al.[-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e. there is no evidence for a relationship. 
However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with `r perc_atleast_1`% of teams reported to have found at least one statistically reliable effect. 
This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r 1-perc_atleast_1`%, with the majority of teams not detecting the effect. 
If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us). 
Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to a broad research question.

>>>>

**Non-preregistered**. However, in our preregistration we did not take into account that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption. 
Teams were explicitly instructed to only submit one effect size without enforcing it. 
As a result, some teams followed the instruction and submitted only one model while others submitted multiple models.
To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (`(1|team) + (1|team:model_id)`), which allows us to estimate both the between-team variation and the between-analysis variation.
This analysis was not preregistered and should thus be interpreted with caution.^[Note that before fitting this model, we fitted a separate one in which model ID was the only (non-nested) group-level effect. 
The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.]

@@

After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
The meta-analytic model estimates the range of probable values of the standardized effect size to be between `r round(meta_intercept_prereg[3],3)` and `r round(meta_intercept_prereg[4],3)` standard units (95\% CrI, mean = `r round(meta_intercept_prereg[1],3)`).
In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g. by duration, f0, etc,) or, if they do, they do so by a maximum of `r pm(x = 0.03)` standard units.

**Non-preregistered**. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
In this non-preregistered model, the meta-analytic intercept estimate is between `r round(meta_intercept_nest[3],3)` and `r round(meta_intercept_nest[4],3)` standard units (95\% CrI, $\beta$ = `r round(meta_intercept_nest[1],3)`).
This suggests that the acoustic measures of typical word combinations are `r -round(meta_intercept_nest[3],2)` standard units lower to `r round(meta_intercept_nest[4],2)` standard units higher than the measures of atypical word combinations, at 95% confidence.
This result is qualitatively similar to the results obtained in the preregistered model.

@@

While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e. are compatible with a point null hypothesis), there are `r compelling_count_nest[[1]] + compelling_count_nest[[3]]` model estimates for which the 95\% credible interval does not contain zero (in orange, `r round((compelling_results_nest[[1,1]] + compelling_results_nest[[3,1]]), 2) * 100`\%).

@@

@@

Different analysis paths led to different categorical conclusions with `r round(perc_atleast_1, 1)`% of teams reported to have found at least one statistically reliable effect.
To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows. 
These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.^[Note that these categories necessarily refer to a variegated set of measures, for example the domain "word" includes words that differed along several dimensions, including their length and their metrical structure.]

```{r ms}
meta_low <- round(meta_bm_nest_tidy$conf.low[["sd_animal:model_id__Intercept"]], 2)
meta_high <- round(meta_bm_nest_tidy$conf.high[["sd_animal:model_id__Intercept"]], 2)

ms_low <- round(min(msa_models$estimate) * round(msa_sd$sd_min[1], 1), 2)
ms_high <- round(max(msa_models$estimate) * round(msa_sd$sd_min[1], 1), 2)

ms_sd_min <- round(msa_sd$sd_min[1], 1)
ms_sd_max <- round(msa_sd$sd_max[1], 1)

ms_meta_low <- round(ms_sd_min * meta_low * 1.96, 1)
ms_meta_high <- round(ms_sd_max * meta_high * 1.96, 1)
```

For example, for those analyses that investigated the duration of vowels (e.g. the duration of the stressed vowel in *Banáne*), the reported duration measures exhibit standard deviations that range from `r ms_sd_min` to `r ms_sd_max` ms.
These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
The reported effect estimates from teams varied between `r round(min(msa_models$estimate),2)` and `r round(max(msa_models$estimate),2)` standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from `r ms_low` to `r ms_high` ms.
A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between `r ms_meta_low` and `r ms_meta_high` ms at 95% credibility.
The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95% CrI of the between-models variability estimate, times 1.96 to obtain a 95% CrI: `r ms_sd_min` * `r meta_low` * 1.96 = `r ms_meta_low` ms; the maximum standard deviation of duration multiplied by the upper limit of the 95% CrI of the between-models variability estimate, times 1.96: `r ms_sd_max` * `r meta_high` * 1.96 = `r ms_meta_high` ms.

While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms [@nicenboim2018using]. 
This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations [@port2005against] and has been replicated several times in both production and perception.
Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts [@coretta2019], reduction phenomena [@nowak2006], and biomechanical reflexes of prominence [@mucke2014effect]. 
Thus, variation between different analyst teams of `r ms_meta_low` to `r ms_meta_high` ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions. 
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates: 
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations. 
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e. mean, mininum, maximum, or range) and how their statistical model was constructed (i.e. the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4). 
As shown by Breznau et al. [-@breznau2021observing], even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e. there is no evidence for a relationship. 
However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with `r round(perc_atleast_1, 1)`% of teams reported to have found at least one statistically reliable effect. 
This rate is substantially higher than the conventionally accepted 5% false positive rate in for example null hypothesis significance testing frameworks.
If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of `r round(1-perc_atleast_1, 1)`%, with the majority of teams not detecting the effect. 
If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us). 
Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to a broad research question.

### 2023-01-19 RR_manuscript/Draft_RR.tex

\textbf{Non-preregistered}. However, in our preregistration we did not take into account that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption.
Teams were explicitly instructed to only submit one effect size without enforcing it.
As a result, some teams followed the instruction and submitted only one model while others submitted multiple models.
To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id)}), which allows us to estimate both the between-team variation and the between-analysis variation.
This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before fitting this model, we fit a separate one in which model ID was the only (non-nested) group-level effect.
  The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.}

@@

After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.026 and 0.016 standard units (95\% CrI, mean = -0.005).
In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.02\) standard units.

\textbf{Non-preregistered}. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
In this non-preregistered model, the meta-analytic intercept estimate is between -0.016 and 0.03 standard units (95\% CrI, \(\beta\) = 0.008).
This suggests that the acoustic measures of typical word combinations are 0.01 standard units lower to 0.04 standard units higher than the measures of atypical word combinations, at 95\% confidence.
Relative to the preregistered model, this model suggests a somewhat positive effect of typicality (although small negative effects are also possible).

@@

While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in blue, 14\%).

@@

Different analysis paths led to different categorical conclusions with 39.3939394\% of teams reported to have found at least one statistically reliable effect.
To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows.
These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.\footnote{Note that these categories necessarily refer to a variegated set of measures, for example the domain ``word'' includes words that differed along several dimensions, including their length and their metrical structure.}

For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banane}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
These standard deviations allow us to convert the meta analytic estimates into milliseconds by multiplying those values with the standard units.
The reported effect estimates from teams varied between -0.7 and 1.01 standard units, which corresponds to duration values ranging from -23.34 to 52.07 ms.
A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.4 and 15.1 ms at 95\% credibility.\footnote{The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: \(33.4 * 0.11 = 3.8\), \(3.8 * 1.96 = 7.4\) ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: \(51.4 * 0.15 = 7.7\), \(7.7 * 1.96 = 15.1\) ms.}

While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}.
This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against} and has been replicated several times in both production and perception.
Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts \citep{coretta2019}, reduction phenomena \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
Thus, variation between different analyst teams of 7 to 15 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
As shown by Breznau et al.\citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e.~there is no evidence for a relationship.
However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 39.3939394\% of teams reported to have found at least one statistically reliable effect.
This rate is substantially higher than the conventionally accepted 5\% false positive rate in for example null hypothesis significance testing frameworks.
If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -38.3939394\%, with the majority of teams not detecting the effect.
If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to a broad research question.

>>>>

\textbf{Non-preregistered}. However, in our preregistration we did not take into account that teams might submit multiple analyses/models which, if unaccounted for, violates the independence assumption.
Teams were explicitly instructed to only submit one effect size without enforcing it.
As a result, some teams followed the instruction and submitted only one model while others submitted multiple models.
To account for this added layer of dependency, we have run a model with team and model ID nested within team as group-level effects (\texttt{(1\textbar{}team)\ +\ (1\textbar{}team:model\_id)}), which allows us to estimate both the between-team variation and the between-analysis variation.
This analysis was not preregistered and should thus be interpreted with caution.\footnote{Note that before fitting this model, we fitted a separate one in which model ID was the only (non-nested) group-level effect.
  The estimated group-level effect of model ID is identical to that of the nested model, so we will not discuss it further.}

@@

After assessing the variation between teams and analyses, we now turn to the meta-analytic estimate of the effect of typicality on the acoustic realization of sentences with adjective-noun combinations.
The meta-analytic model estimates the range of probable values of the standardized effect size to be between -0.026 and 0.016 standard units (95\% CrI, mean = -0.005).
In other words, our best guess is that speakers might not encode typicality in the acoustic signal (e.g.~by duration, f0, etc,) or, if they do, they do so by a maximum of \(\pm 0.03\) standard units.

\textbf{Non-preregistered}. As mentioned in the previous section, we have run an additional model, using team and model ID nested within team as group-level effects.
In this non-preregistered model, the meta-analytic intercept estimate is between -0.016 and 0.03 standard units (95\% CrI, \(\beta\) = 0.008).
This suggests that the acoustic measures of typical word combinations are 0.02 standard units lower to 0.03 standard units higher than the measures of atypical word combinations, at 95\% confidence.
This result is qualitatively similar to the results obtained in the preregistered model.

@@

While the majority of model estimates and their uncertainty after shrinkage (in black) yields inconclusive results (i.e.~are compatible with a point null hypothesis), there are 27 model estimates for which the 95\% credible interval does not contain zero (in orange, 14\%).

@@

Different analysis paths led to different categorical conclusions with 39.4\% of teams reported to have found at least one statistically reliable effect.
To gain a better understanding of whether the observed quantitative variability can result in theoretically different claims, we will contextualize them in actual acoustic measures.
We calculated the standard deviation of a selection of acoustic measurements, as submitted by the analysis teams: duration, f0 and intensity, taken from different time windows.
These standard deviations can be considered as a coarse indication of the variability in the obtained acoustic measures.
We can now use these values to interpret the meta-analytic estimates, which are in standardized units, by transforming the standardized units to measures of duration, f0 and intensity.\footnote{Note that these categories necessarily refer to a variegated set of measures, for example the domain ``word'' includes words that differed along several dimensions, including their length and their metrical structure.}

For example, for those analyses that investigated the duration of vowels (e.g.~the duration of the stressed vowel in \emph{Banáne}), the reported duration measures exhibit standard deviations that range from 33.4 to 51.4 ms.
These standard deviations allow us to convert the meta-analytic estimates into milliseconds by multiplying those values with the meta-analytic estimates standard units.
The reported effect estimates from teams varied between -0.7 and 1.01 standard units, which corresponds to estimated segment duration differences (for atypical vs typical combinations) ranging from -23.34 to 33.84 ms.
A more conservative approach is to convert the meta-analytic estimates of between-model variation, thus obtaining an estimate of between-model variability in milliseconds that ranges between 7.2 and 14.1 ms at 95\% credibility.
The calculation is thus: the minimum standard deviation of duration multiplied by the lower limit of the 95\% CrI of the between-models variability estimate, times 1.96 to obtain a 95\% CrI: 33.4 * 0.11 * 1.96 = 7.2 ms; the maximum standard deviation of duration multiplied by the upper limit of the 95\% CrI of the between-models variability estimate, times 1.96: 51.4 * 0.14 * 1.96 = 14.1 ms.

While this might not immediately strike one as highly variable, it crosses several theoretically relevant thresholds for perception and articulation:
for example, the widely studied phenomenon of incomplete neutralization involves vowel duration effects ranging from 7 to 15 ms \citep{nicenboim2018using}.
This particular phenomenon has sparked long-lasting methodological and theoretical debates about the very nature of linguistic representations \citep{port2005against} and has been replicated several times in both production and perception.
Vowel duration differences within this range have also been reported across phenomena associated with segmental contrasts \citep{coretta2019}, reduction phenomena \citep{nowak2006}, and biomechanical reflexes of prominence \citep{mucke2014effect}.
Thus, variation between different analyst teams of 7.2 to 14.1 ms in one or the other direction can be theoretically relevant and might lead to opposing theoretical conclusions.

@@

While one might find it obvious that measuring different parts of the speech signal can lead to different results, the fact that analysts (and reviewer alike) considered all these data analytic pipelines valid ways of answering the same research question points to a lack of theoretical consensus on what parts of the speech signal correspond to what types of communicative functions.
Importantly, even if analysts choose to measure more or less the same acoustic property within the same measurement window, they arrive at different estimates:
For example, six teams measured f0 in the adjective and predicted f0 based on typicality as a categorical predictor. Their standardized effect estimates ranged from -0.11 to 0.38 standard deviations.
While these teams in principle measured the same thing, they differed in analytical details of how f0 was operationalized (i.e.~mean, mininum, maximum, or range) and how their statistical model was constructed (i.e.~the number of predictors ranged from 1-3 and the number of random effect terms ranged from 1-4).
As shown by Breznau et al. \citeyearpar{breznau2021observing}, even seemingly inconsequential analytical choices can affect conclusions in non-trivial ways.

@@

Looking at our results, one might argue (and this interpretation has been articulated by several teams during the collaborative write-up) that our sample of speech scientists actually converged on a qualitative conclusion, i.e.~there is no evidence for a relationship.
However, if there truly was no underlying relationship, our results would suggest a concerning false positive rate with 39.4\% of teams reported to have found at least one statistically reliable effect.
This rate is substantially higher than the conventionally accepted 5\% false positive rate in for example null hypothesis significance testing frameworks.
If, on the other hand, there actually was an underlying relationship, our results would suggest a concerning false negative rate of -38.4\%, with the majority of teams not detecting the effect.
If the latter was true, the fact that the majority of teams arrived at a null result might also simply be a consequence of the sample size in the data set being too small to reliably detect an effect (which is unknown to us).
Thus, we do not think that our study provides convincing evidence that speech researchers converged on the same qualitative answer to a broad research question.
